%-------------------------------------------------------------------------
\documentclass[report,english,cleveref,autoref,a4paper]{lipics-v2021}
%-------------------------------------------------------------------------
\hideLIPIcs
\bibliographystyle{plainurl}
\usepackage{array}
\usepackage{colortbl}
\usepackage[dvipsnames]{xcolor}
\newcommand{\grayhline}{\arrayrulecolor{lightgray}\hline\arrayrulecolor{black}}
\newcommand{\graycline}[2]{\arrayrulecolor{lightgray}\cline{#1-#2}\arrayrulecolor{black}}
\nolinenumbers
%-------------------------------------------------------------------------


%-------------------------------------------------------------------------
\newcommand{\myname}{Amir Nurmukhambetov}             % your full name
\newcommand{\myshortname}{A.N.~Nurmukhambetov}             % your name with abbreviated first name(s)
\newcommand{\mystudentid}{1930907}                % put your student id here
\newcommand{\mysupervisor}{Prof.\ M.J.M.\ Roeloffzen}
\newif\ifGuidelines
\Guidelinestrue
% \textbf{}\Guidelinesfalse                                  % uncomment when submitting your portfolio
\ifGuidelines
    \newcommand{\explanation}[1]{\emph{Explanation:} #1}
\else 
    \newcommand{\explanation}[1]{}
\fi
%-------------------------------------------------------------------------


%-------------------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------------------

\ifGuidelines
%-------------------------------------------------------------------------
\section*{Guidelines for Bachelor End Projects in the ALGO Cluster}
\thispagestyle{empty}
%-------------------------------------------------------------------------
This document describes the set-up of Bachelor End Projects in the ALGO cluster.
The document also provides a template for your portfolio.


%-------------------------------------------------------------------------
\subparagraph{Supervision and execution.}
%-------------------------------------------------------------------------
Bachelor End Projects (BEPs) are individual research-oriented projects.
The execution of the BEP should be done in an independent manner: the role of the
supervisor is to monitor that you do not go into the wrong direction and to give
you suggestions and feedback, not to help you solve the problem or debug your code. 

BEPs are organized in \emph{circles}: groups of up to six students with the
same supervisor and with a similar topic for their project. Each circle meets
several times with their supervisor; see below for a detailed schedule. 
During these meetings, students report on their progress and the
supervisor can give suggestions on how to proceed. Students can also learn
from other students or give them suggestions. Students may also help each other 
outside the circle meetings. However, BEPs are individual projects, so students should 
never share code or text, unless explicitly allowed by the supervisor.
When using code or other material from external sources, this should
be properly referenced in your final report.

%-------------------------------------------------------------------------
\subparagraph{Deliverables.}
%-------------------------------------------------------------------------
There are four written deliverables:
\begin{itemize}
	\item An initial \emph{project plan}, including time planning, milestones, and risk mitigation strategies. 
	\item A \emph{midterm report} on the status of the BEP after the first quartile, an updated planning, 
          and a draft version of a part of the final report. This draft version typically contains 
          most of the introduction and possibly a description of the algorithms that you have developed 
          and/or algorithms from the literature that you will use in your experiments. \emph{Discuss 
          with your supervisor what is expected from you.}
	\item The \emph{final report}, which should be at most 400 lines. See the template for
          additional guidelines.
	\item A \emph{reflection}, where you reflect on the planning, process, choices made during the project, and what you learned from it.
\end{itemize}
The fifth deliverable is the presentation, which will take place in the exam week of Q4.

The written deliverables are combined into a single \emph{portfolio} that you must submit near the end
of the course through Canvas. For archival purposes, you must also submit your initial planning, 
your midterm report, and your final report through Canvas during the course; see the schedule below for deadlines.
Note that the final portfolio must still include the initial project plan, the midterm report, and the final report.

%-------------------------------------------------------------------------
\subparagraph{Time sheets.}
%-------------------------------------------------------------------------
It is mandatory to maintain a time sheet in which you describe the activities 
you performed and how much time you spent on them during each week of 
the project. This helps you to keep track of how much time you spent on the 
project---note that you are supposed to spend about 14 hours per week on the BEP---and if the time investment 
for the various parts of the project is in line with your planning.
This is also useful at the end of the project, when you have to write a reflection.
Make your time sheets concrete. 
Here is  an example.
\\ \\
\begin{tabular}{c| m{10cm}|c}
\hline\hline
Q1: week 7  & Circle meeting & 1.5 hours \\
\cline{2-3}
     & Polished motivation and problem statement, and
     related work, in Section~1 of the final report. & 2 hours \\
\cline{2-3}
     & Finished first draft of Section 2.1 of the final report. & 6 hours \\
\cline{2-3}
     & Continued with the implementation of the greedy algorithm  & 4 hours \\
\cline{2-3}
     & \multicolumn{1}{r|}{week total} & 13.5 hours \\
\hline \hline
\end{tabular}


%-------------------------------------------------------------------------
\subparagraph{Overleaf and git.}
%-------------------------------------------------------------------------
Your portfolio must be written in \LaTeX{} using the provided template---see below---and
you must use Overleaf (\url{https://www.overleaf.com/}). You should create a new
project on Overleaf, named \texttt{ALGO-BEP-yyyy-name}, where \texttt{yyyy} is 
the current year and \texttt{name} is your last name. After creating the project
on Overleaf, you must invite your supervisor to the project. If you prefer to
edit in a different environment than in Overleaf itself, you must update
the Overleaf files every day that you have worked on the files.
There is also a separate template for the time sheets, which must be maintained in Overleaf as well
(in the same project).
\begin{quote}
\noindent \textbf{It is important that you work on your final report throughout the project:
already write the motivation and problem statement and the related-work part of
the introduction early on, write a description of your algorithms before implementing them,
and so on.}
\end{quote}
For your code you must use \url{https://gitlab.tue.nl/users/sign_in} and make sure
your supervisor has access to your repository.


%-------------------------------------------------------------------------
\subparagraph{Plagiarism and AI usage.}
%-------------------------------------------------------------------------
As already mentioned, you should not use code or text from other students
(unless explicitly allowed). The same is true for code or text from other sources:
before you use material from other sources, you must always ask permission from your supervisor.

As for AI usage: it is allowed to use AI tools to make small improvements in
the text you have written---in particular, it is allowed to use {\sc writefull} on
Overleaf---but it is not allowed to use AI tools to generate entire paragraphs.
Similarly, you can use AI tools to debug your own code or to generate small code snippets,
but not to generate long pieces of code.

%-------------------------------------------------------------------------
\subparagraph{Communication during the course.}
%-------------------------------------------------------------------------
Communication with the supervisor will mainly be done via the circle meetings.
There will also be a Slack channel for each circle. The main goal of the 
Slack channel will be to facilitate communication between students in the circle.
You may also ask questions to the supervisor in the channel, but supervisors
may not respond immediately or they may defer answering the questions to the
next circle meeting.

%-------------------------------------------------------------------------
\subparagraph{Meeting schedule.}
%-------------------------------------------------------------------------
Below is the meeting schedule for the BEPS in Q3+Q4 of the academic year 25/26.
Some remarks:
\begin{itemize}
\item Attending \emph{all} circle meetings (in person) is mandatory.
\item Deadlines for the deliverables are in \textcolor{red}{red}. These delivarables
should be submitted through the appropriate Assignment in Canvas.
\item Other ``submissions'' (draft versions, time sheets) do not have to be done through
       Canvas; just make sure that they are available through Overleaf (that is,
       make sure that your documents in Overleaf are up-to-date and contain
       the required items).
\item The weeks of the circle meetings may deviate from the general schedule below.
The exact schedule (including the day and time of the meetings) is determined by your supervisor.
\end{itemize}
%-------------------------------------------------------------------------
\begin{tabular}{c|r|l|l|l}
quartile & week & dates & meetings & deadlines for deliverables \\
\hline
Q3  & 1 & Feb 2--6 & Kickoff meeting &   \\
\graycline{2}{5}
    & 2 & Feb 9--13 & Circle meeting & \parbox[c][12mm][c]{50mm}{\textcolor{red}{Friday, Feb 13, 23:59} \\ Initial planning} \\
\graycline{2}{5}
    &  \multicolumn{4}{c}{\emph{Carnaval week}}  \\
\graycline{2}{5}
    & 3 & Feb 23--27 &  &  \\
\graycline{2}{5}
    & 4 & March 2--6 & Circle meeting & \\
\graycline{2}{5}
    & 5 &  Mar 9--13 &  & \\
\graycline{2}{5}
    & 6 & Mar 16--20 &  & \\
\graycline{2}{5}
    & 7 & Mar 23--27 & Circle meeting & \\
\graycline{2}{5}
    & 8 & Mar 30 -- Apr 3 &  &  \\
\graycline{2}{5}
    & 9 & Apr 6--10 & \emph{Exam week} & \parbox[c][17mm][c]{50mm}{\textcolor{red}{Friday, Apr 10, 23:59} \\ Midterm report \\ (including updated planning)} \\
\graycline{2}{5}
    & 10 & Apr 13--17 &  \multicolumn{2}{c}{\emph{Exam week} \hspace*{40mm}}  \\
\hline
Q4  & 1 & Apr 20--24 & Circle meeting & \\
\graycline{2}{5}
    & 2 & Apr 27 -- May 1 &  & \\
\graycline{2}{5}
    & 3 & May 4--8 &  &  \parbox[c][12mm][c]{50mm}{Friday, May 8, 23:59 \\ Draft 1.0 of final report}\\
\graycline{2}{5}
    & 4 & May 11--15 & Circle meeting & \\
\graycline{2}{5}
    & 5 & May 18--22 &  & \\
\graycline{2}{5}
    & 6 & May 25--29 &  & \\
\graycline{2}{5}
    & 7 & Jun 1--5 &  &  \parbox[c][12mm][c]{50mm}{Wednesday, June 3, 23:59 \\ Complete draft of final report} \\
\graycline{2}{5}
    & 8 & Jun 8--12  & Circle meeting & \parbox[c][12mm][c]{50mm}{\textcolor{red}{Friday, June 12, 23:59} \\ Final report}\\
\graycline{2}{5}
    & 9 & Jun 15--19  &  & \parbox[c][17mm][c]{50mm}{\textcolor{red}{Friday, June 19, 23:59} \\ Complete portfolio\\(including reflection)} \\ 
\cline{2-5}
    & 10 & Jun 22--26 &  \multicolumn{2}{c}{\emph{Exam week:} Final presentations}  \\
    & 11 & Jun 29 -- Jul 3 &  \multicolumn{2}{c}{\emph{Exam week:} Final presentations}  \\
\hline
\end{tabular}
%-------------------------------------------------------------------------


%-------------------------------------------------------------------------
\subparagraph{How to use this document as a template for your portfolio.} 
%-------------------------------------------------------------------------
To use this template, insert your full name, name with abbreviated first names,
student id, and name of your supervisor in the relevant place in the {\LaTeX} source file 
(lines 11, 12, and 13).
Before submitting, un-comment \texttt{\textbackslash{}Guidelinesfalse} on line~18.
\emph{Using the template is mandatory; do not change the document class and do not
make changes to the layout.}

\newpage
%-------------------------------------------------------------------------
\else                                           % do not show guidelines
\fi
%-------------------------------------------------------------------------

%-------------------------------------------------------------------------
\title{PORTFOLIO Bachelor Final Project (2ICS00)}
%-------------------------------------------------------------------------
\author{Student: \myname~(\mystudentid)}{Eindhoven University of Technology}{}{}{}
\author{Supervisor: \mysupervisor~(ALGO)}{$\mbox{}$}{}{}{}
\authorrunning{\myshortname}
%-------------------------------------------------------------------------

%-------------------------------------------------------------------------
\maketitle
\newpage
%-------------------------------------------------------------------------

%-------------------------------------------------------------------------
\setcounter{page}{1}
\tableofcontents
\newpage
%-------------------------------------------------------------------------

%-------------------------------------------------------------------------
\part{Process Documents}
\label{part:process}
\setcounter{page}{1}
\thispagestyle{empty}
\newpage
%-------------------------------------------------------------------------

%-------------------------------------------------------------------------
\section{Project description and initial planning (max 2 pages)}
%-------------------------------------------------------------------------

%-------------------------------------------------------------------------
\subsection{Project description}
\label{subsec:project}
%-------------------------------------------------------------------------
% \explanation{Clearly describe the problem(s) you plan to investigate, the scientific and/or
% societal or industrial relevance, and the goal(s) of the project.}

Time-constrained TSP is a variant of the Traveling Sailsman Problem in which given an upper bound $L$ the total length of the tour and each point in the input set $P$ is assigned a value of $v(p)$. The objective is to find a tour of total length of at most $L$ and visit a subset of points whose total value is maxmized. 
\\ \\
In this project, I'll consider an extension of time-constrained TSP in which visiting a point $p$ replenishes the remaining travel budget $L$ with a function $r(p)$. I'll investigate existing algorithmic approaches and performance under realistic constraints, including a maximum travel budget (capacity) $L$.

\subsubsection{Relevance}

This problem is relevant to transportation logistics. Consider a vehicle transporting goods with a limited fuel capacity. The driver must choose which drop-off locations to service in order to maximize total profit (e.g., payment per delivery) while remaining fuel-feasible. Along the route, the vehicle may stop at designated refueling locations (such as gas stations or depots) that replenish fuel, typically up to the tank capacity. Here the travel budget corresponds to fuel, and $r(p)$ models models the amount of fuel regained when refueling at location $p$.

\subsubsection{Goal}

The goal of this project is to extend time-constrained TSP formulations by introducing refueling decisions with a hard capacity limit, and to evaluate the approach by comparing it with existing methods on logistics-style benchmark instances.

\subsubsection{Scope}

The project will consider heuristic solution approaches for the time-constrained TSP and related prize-collecting routing problems. In particular, as baseline methods, I will (i) implement a mixed-integer linear program (MILP) for the prize-collecting problem, and (ii) implement an expanded-graph (state-space) baseline for the refueling variant by discretizing fuel into levels, then (iii) I will solve the resulting model using a MILP to obtain a strong baseline for comparison.
\\ \\
On these baselines, I will implement improvement heuristics, including 2-opt/3-opt route polishing and prize-aware neighborhood moves (e.g., add/drop/swap) while maintaining feasibility with respect to both the length budget and refueling dynamics.
\\ \\
Experiments will be conducted on synthetic logistics-style instances, and will report collected reward value, feasibility, and computational runtime.

%-------------------------------------------------------------------------
\subsection{Planning}
\label{subsec:planning}
%-------------------------------------------------------------------------
% \explanation{Give a planning for the project. Make sure you include all relevant aspects (for
% experimental projects this could include: literature study, 
% design and/or theoretical analysis of algorithms, implementation of algorithms, generation of test sets,
% performing experiments, evaluation of the outcome of the experiments, writing of the final report, preparation
% of the final presentation.}

The BEP spans two quartiles (Q3 and Q4). The planning below is organized per week. I'm planning to work on report throughout the the whole process documenting steps along the way.

\subsubsection{Q3: Literature study, Greedy Heuristic, and Dataset Design}

\begin{itemize}
  \item \textbf{Week 1 -- 4: Literature Study \& Greedy Baseline}
  \begin{itemize}
    \item Study literature on the Prize-Collecting TSP, Orienteering Problem, and common heuristics (local search, metaheuristics).
    \item Implement a greedy insertion heuristic (value-to-cost ratio) as a fast baseline.
    \item Develop core C++ infrastructure: instance representation, distance calculations, and solution I/O.
  \end{itemize}

  \item \textbf{Week 5 -- 8: Dataset Generation Design \& Midterm Report}
  \begin{itemize}
    \item Design a strategy for generating varied and challenging datasets, including uniformly random and clustered (Gaussian Mixture Model) point distributions.
    \item Prepare the midterm report, documenting the pivot, the implemented greedy heuristic, and the updated plan for Q4.
  \end{itemize}
  
  \item \textbf{Week 9 -- 10: Buffer and Finalize Dataset Generator}
  \begin{itemize}
    \item Address any feedback from the midterm report.
    \item Implement the Python-based dataset generator script.
  \end{itemize}
\end{itemize}

\subsubsection{Q4: Advanced Heuristics, Experiments, and Final Report}

\begin{itemize}
  \item \textbf{Week 1 -- 3: Local Search Implementation}
  \begin{itemize}
    \item Implement a 2-opt local search procedure to improve solutions from the greedy heuristic.
    \item Test and debug the local search on small instances.
  \end{itemize}
  
  \item \textbf{Week 4 -- 6: Genetic Algorithm Implementation}
  \begin{itemize}
    \item Design and implement a Genetic Algorithm (GA). This will include defining crossover and mutation operators suitable for permutation-based solutions.
    \item Integrate the 2-opt local search as a solution improvement step within the GA (memetic algorithm).
  \end{itemize}
  
  \item \textbf{Week 7 -- 8: Experimental Campaign \& Analysis}
  \begin{itemize}
    \item Run comprehensive experiments comparing the greedy, greedy + 2-opt, and GA approaches across all generated datasets.
    \item Analyze the results, focusing on solution quality (total value) versus runtime.
  \end{itemize}

  \item \textbf{Week 9 -- 10: Final Report and Presentation}
  \begin{itemize}
    \item Write the final report, detailing the algorithms, experimental setup, and results.
    \item Prepare and rehearse the final presentation.
  \end{itemize}
\end{itemize}


%-------------------------------------------------------------------------
\section{Midterm status report (max 1 page)}
%-------------------------------------------------------------------------
\textbf{Overview of Progress:}
Work so far has focused on establishing a baseline for the Time-Constrained TSP. A greedy heuristic, which iteratively adds nodes based on the best value-to-insertion-cost ratio while respecting the length budget `L`, has been successfully implemented in C++. The necessary infrastructure for instance generation, distance calculations (respecting adjacency), and solution output is also complete.
\\ \\
\textbf{Difficulties and Pivot:}
The initial plan was to develop a Mixed-Integer Linear Program (MILP) and investigate a variant with refueling stops. However, I have pivoted the project to focus exclusively on developing high-performance heuristics for the standard Time-Constrained TSP. This decision was made for two main reasons:
\begin{enumerate}
    \item The refueling variant adds significant complexity, and focusing on the core problem allows for a deeper and more thorough investigation of advanced heuristics.
    \item MILP-based approaches are generally limited to small instances, whereas the new focus on heuristics (like local search and genetic algorithms) will allow for experiments on larger, more realistic datasets.
\end{enumerate}

\textbf{Remaining Work and Updated Planning:}
The core task for the remainder of the project is to build upon the greedy baseline. The next steps are:
\begin{enumerate}
    \item \textbf{Dataset Generation:} Create structured datasets, particularly clustered instances using Gaussian Mixture Models, to rigorously test algorithm performance. This will be done using a Python script.
    \item \textbf{Local Search:} Implement a 2-opt local search heuristic to improve the solutions found by the greedy algorithm.
    \item \textbf{Metaheuristic:} Develop a Genetic Algorithm to find high-quality solutions, likely incorporating the local search as an improvement step.
    \item \textbf{Experimental Evaluation:} Conduct a comprehensive experimental campaign to compare the performance of the greedy, local search, and genetic algorithms across the generated datasets.
\end{enumerate}

%-------------------------------------------------------------------------
\section{Reflection (max 1 page)}
%-------------------------------------------------------------------------
\explanation{Reflect on your execution of the project: What did you learn? 
Which part of the research went as you anticipated and which parts did not?
Would you do anything differently, if you had to do a similar project again?}





%-------------------------------------------------------------------------
\newpage
%-------------------------------------------------------------------------


%-------------------------------------------------------------------------
\part{Report}
\label{part:report}
%-------------------------------------------------------------------------
\newpage
%-------------------------------------------------------------------------

%-------------------------------------------------------------------------
\setcounter{section}{0}
\setcounter{page}{1}
\thispagestyle{empty}
\section*{Comparison between Heuristic Algorithms for the Time-Constrained Traveling Salesman Problem}
\textbf{\myname}

\linenumbers
%-------------------------------------------------------------------------


%-------------------------------------------------------------------------
\begin{abstract}

\explanation{Briefly describe the problem that you have studied and the main results
and conclusions of your work. Typically the abstract consists of a single
paragraph of about 5--10 lines.}

TODO

\end{abstract}
%-------------------------------------------------------------------------



%-------------------------------------------------------------------------
\section{Introduction}
\label{sec:intro}
%-------------------------------------------------------------------------
% \explanation{Typically 1.5--2 pages.}

\subparagraph{Motivation and problem statement.}

% \explanation{Give a motivation for the problem you will study. 
% Often you can do this by discussing a real-world application
% that is related to your problem.  After that, you can describe how the problem 
% can be abstracted, to arrive at your problem.
% (In some cases, it may be more appropriate to motivate the problem 
% from a purely scientific rather than an applied perspective.)
% Make sure that your problem statement is unambiguous and clear.}

Modern logistics networks increasingly demand efficient route planning
under real-world operational constraints. Consider a courier operating
a same-day delivery service: departing from a central depot, the vehicle
must return before a hard deadline imposed by fuel capacity, battery
limitations, or working-hour regulations. Because the number of
potential delivery locations typically exceeds what can be served within
these constraints, the dispatcher faces a combinatorial decision: which
subset of customers to visit, and in what order, so as to maximise the
total collected value---whether measured in revenue, number of parcels,
or customer priority score. In this setting, the selection of delivery points
and the underlying routing problem is generally known as the \textbf{Time-Constrained 
Traveling Salesman Problem} (TTSP) or the \textbf{Orienteering Problem}. In general, the
TTSP is defined by:

\begin{itemize}
\item A set of candidate locations (e.g., delivery points), each associated with a profit or value.
\item The travel time between locations.
\item A hard constraint on the total distance (or time) of the tour, reflecting operational constraints.
\end{itemize}

This situation is by no means unique to delivery logistics. Similar
trade-offs arise in autonomous vehicle routing~\cite{}, drone-based
infrastructure inspection~\cite{}, and mobile tourist guidance~\cite{},
where a tour must be planned for a visitor who can only explore a subset
of points of interest (POIs) within a limited time budget~\cite{Vansteenwegen2007}.
In each case, the common behaviour is the same: a set of candidate
locations, each carrying a profit, and a hard bound on the total
distance (or time) of the tour.

In the paper, .

The paper is structured as follows: \textbf{TODO}

\subparagraph{Related work.}
% \explanation{Discuss what is known in the literature about your problem and 
% any relevant, closely related, problems. For each paper that you discuss, 
% make it clear which problem variant they solve, 
% and try to be as explicit about the results as possible. 

% Structure the discussion in such a way that the relation between the papers is clear.
% For example, a paper may study exactly the same problem as another paper but
% obtain a better result, or they may study a more general version of the problem.}

The TTSP is formalized and defined as follows: on a set of points in the
Euclidean plane. Given an upper bound $L$ on the total length of the tour,
each point in the input set $P \subset \mathbb{R}^2$ is assigned a 
value of $v(p)$. The objective is to find a tour of total length at 
most $L$ that visits a subset of points whose total value is maximized. This section
introduces the different variants of the problem that have been defined in literature.

For example Vansteenwegen et al.~\cite{} extends the basic model with practical attributes 
such as points of interests (POI) opening hours and visit durations. \textbf{TODO Expand}

Another variant defined by Sebastia and Marzal~\cite{} incorporate travel-style preferences into account. \textbf{TODO Expand}

\subparagraph{Contributions.}
% \explanation{Give a summary of your work, and relate it to what is known in the literature.
% This would typically be one or two paragraphs.
% \\[5mm]
% \emph{Note:} The template below is written with a project in mind that has an experimental
% component. For other types of projects, many of the guidelines given below still apply,
% but the structure would be slightly different;
% please discuss with your supervisor what is expected.}

\textbf{TODO}

%-------------------------------------------------------------------------
\section{The algorithms}
\label{sec:algorithms}
%-------------------------------------------------------------------------

%-------------------------------------------------------------------------
\subsection{Description of the algorithms}
\label{subsec:description}
%-------------------------------------------------------------------------
% \explanation{Describe the algorithms that you developed and/or relevant algorithms
% from the literature. Often this is done best using high-level (that is, not too detailed)
% pseudocode plus a textual explanation. For algorithms from the literature, discuss with 
% your supervisor in how much detail they should be presented.}

\subsubsection{Greedy Baseline}

The implemented problem setting uses node~0 as the depot, while every other node
has an associated reward value. Distances are Euclidean on the edges that are
allowed by the instance, and an edge that is not present in the adjacency
structure is treated as infeasible. A tour is therefore feasible only if every
edge used by the tour exists and the total length of the closed tour, including
the return to the depot, is at most the budget~$L$.

As a first baseline, I implemented a greedy insertion heuristic that builds a
tour incrementally. The algorithm starts with the trivial tour containing only
the depot. In every iteration, it considers each node that is not yet in the
tour and tests all possible insertion positions between two consecutive tour
vertices $a$ and $b$. For a candidate node $v$, the additional travel cost of
inserting $v$ between $a$ and $b$ is computed as
$d(a,v)+d(v,b)-d(a,b)$. For each node, the algorithm keeps only the insertion
position with minimum additional cost, and then assigns the node a score equal
to its reward divided by this cost. After that, the algorithm simulates the
corresponding insertion and checks whether the resulting closed tour is still
feasible with respect to the budget~$L$. Among all feasible candidates, it
selects the node with the highest reward-to-cost ratio, inserts it at the best
position, and repeats this process until no further feasible insertion exists.

The purpose of this heuristic is to provide a fast constructive method that
balances the benefit of visiting a node against the extra travel needed to
include it in the tour. At the same time, the method is inherently myopic,
because every decision is based only on the current tour and the locally best
insertion score. Consequently, it serves as a practical baseline, but it does
not guarantee an optimal solution.
This section describes and introduces several algorithms and approaches of that were used.

\subsubsection{Local Search}

\subsubsection{Genetic Algorithm}

%-------------------------------------------------------------------------
\subsection{Analysis of the algorithms}
\label{subsec:analysis}
%-------------------------------------------------------------------------
\explanation{For each of the algorithms that you presented in Section~\ref{subsec:description}
do the following: Analyze the asymptotic running time of your algorithm(s) and, if possible,
prove their correctness. If your algorithm is a heuristic that may sometimes
fail to produce a correct solution, this should be discussed as well.
For optimization problems: discuss the quality of the solutions computed by your algorithm(s).
For algorithms from the literature: discuss with your supervisor in
how much detail you should do the analysis.}

%-------------------------------------------------------------------------
\section{Experimental evaluation}
\label{sec:evaluation}
%-------------------------------------------------------------------------

%-------------------------------------------------------------------------
\subsection{Data sets}
\label{subsec:data}
%-------------------------------------------------------------------------
\explanation{Clearly describe the data sets that you use. If you use
synthetic data sets, describe how they are generated in such a way
that a reader would be able to generate the data sets themselves.
Explain the roles of the parameter(s) used to generate the data sets.
When possible and relevant, add figures of example data sets.
If you use data sets from other sources, provide a reference
to those data sets.}

Data sets are generated with a c script that generates a random planar graph with $n$ nodes,
where $n$ is a parameter. Rudy is the name of the script. I've extended this script to support
generating nodes with reward values as well. 

%-------------------------------------------------------------------------
\subsection{Experiments and discussion}
\label{subsec:experiments}
%-------------------------------------------------------------------------
\explanation{For each experiment, describe the goal (what do you want
to investigate?) and possibly a hypothesis, and the set-up of the experiment.
The report the outcome (typically using graphs, or perhaps a table)
and discuss the outcome. Try to not only say what the outcome is, but also
to explain it. If you see certain strange effects that you cannot explain,
then just say so---this is better than just ignoring the effects.
When possible relate the outcome to the theoretical analysis you did in Section~\ref{subsec:analysis}.}

%-------------------------------------------------------------------------
\section{Concluding remarks}
%-------------------------------------------------------------------------
\explanation{Briefly discuss the results that you obtained, focusing on
strengths and weaknesses, and discuss possible directions for future research.
This would typically be about half a page.}

%-------------------------------------------------------------------------
\bibliography{references}
%-------------------------------------------------------------------------
\explanation{Put your references in the file \texttt{references.bib}. You can cite
books~\cite{clrs-ia-2009}, journal papers~\cite{lt-stpg-79}, or
conference papers~\cite{DBLP:conf/compgeom/Chang0024}. Add a \texttt{doi} 
if possible. DBLP\footnote{\url{https://dblp.org/}} is a good source for finding reliable 
references. Note, however, that the bibtex entries in DBLP for conferences papers sometimes
contain the location and date of the conference in the title; this should be removed.}


%-------------------------------------------------------------------------
\appendix 
\newpage
%-------------------------------------------------------------------------

%-------------------------------------------------------------------------
\section{Appendix: Additional Material}             % remove if not used
%-------------------------------------------------------------------------
\explanation{In some cases it can be useful to put some material,
such as tables with additional experimental results, into an appendix.
Before adding an appendix, discuss this with your supervisor.
Note that the main text should contain all material that is important,
and that the assessment of your work will be done based on the main text.}

%-------------------------------------------------------------------------
\end{document}
%-------------------------------------------------------------------------
